Data Management for LSST Special Programs

### 2023-05-20 sec_intro.tex
Update sec_intro.tex

The three main messages of this document are:
\begin{enumerate}
\item All visits associated with a Special Program should have a region and a program label 
which is propagated to all processed images, catalog data, and alerts (Section~\ref{ssec:sci_labels}).
\item All visits that can be processed by the Prompt pipelines and generate 
alerts should be, in support of time domain and Solar System science goals (Section~\ref{ssec:proc_wfd}).
\item ``Unique and separate" data products should be generated by RDM whenever possible 
(e.g., coadded images and {\tt Object} catalogs that overlap, but are deeper or shallower than, the WFD) 
\end{enumerate}

>>>>

The three main messages of this document are:
\begin{enumerate}
\item All visits associated with a Special Program should have a region and a program label 
which is propagated to all processed images, catalog data, and alerts (Section~\ref{ssec:sci_labels}).
\item All visits that can be processed by the Prompt pipelines and generate 
alerts should be, in support of time domain and Solar System science goals (Section~\ref{ssec:proc_wfd}).
\item ``Unique and separate" data products should be generated by RDM whenever possible 
(e.g., coadded images and {\tt Object} catalogs that overlap, but are deeper or shallower than, the WFD; Section~\ref{ssec:proc_rdm}) 
\end{enumerate}
